\LARGE \bf Matrix Multiplication-Driven Repulsive Fields for Manipulator Kinematic Obstacle Avoidance

### 2024-03-19 Articles/IROS/root.tex
removed more references

Motion planning is a technique in robotics, that is used to calculate joint changes leading manipulators from initial to a target configuration, while addressing constraints and optimization criteria. This task is facilitated by the manipulators' redundant degrees of freedom (DOF), enabling it to undertake various configurations to not only reach their End Effector (EE) target but also optimize for secondary objectives such as obstacle avoidance and minimizing joint torques~\cite{siciliano1990kinematic, siciliano2010robot}.

While global motion planning techniques provide comprehensive solutions by examining the entire configuration space, they fall short in terms of smoothness and real-time application, making them less ideal for dynamic settings~\cite{lavalle1998rapidly, gammell2015batch, karaman2010incremental,kuffner2000rrt}. Conversely, local planning methods, particularly inverse kinematics~\cite{c29,c38} and quadratic programming~\cite{c21,c23}, offer prompt, smooth trajectories suitable for real-time operations. However, these methods are prone to fall into local minima due to their incremental planning approach.

@@

Our approach utilizes occupancy voxel grids to enable safe and dynamic navigation for robot manipulators in changing environments. By representing the workspace with voxels and calculating repulsive velocities based on proximity to obstacles, our method allows the robot to determine safe movement directions and velocities in real-time. Repulsive velocities gain strength as the robot approaches an obstacle, guiding it to move away from potential collisions, and weaken when the robot is at a safe distance, maintaining an optimal distance from hazards. This locally-calculated repulsive field ensures the robot moves safely and efficiently in dynamic environments.

@@

\bibitem{siciliano2010robot} B. Siciliano, L. Sciavicco, L. Villani, and G. Oriolo, Robot. Model. Plan. Control, 2010, pp. 161–189. [Online]. Available: http://link.springer.com/10.1007/978-1-84628-642-1\_4

%\bibitem{vsvestka1997motion} P. {\v{S}}vestka and M. H. Overmars, “Motion planning for carlike robots using a probabilistic learning approach,” The International Journal of Robotics Research, vol. 16, no. 2, pp. 119–143, 1997.

@@

%\bibitem{c22} Y. Zhang, S. S. Ge, and T. H. Lee, “A Unified Quadratic-Programming-Based Dynamical System Approach to Joint Torque Optimization of Physically Constrained Redundant Manipulators,” IEEE Trans. Syst., Man, Cybern. B, vol. 34, no. 5, pp. 2126–2132, Oct. 2004. doi: 10.1109/TSMCB.2004.830347.

@@

%\bibitem{c40} J.-O. Kim and P. Khosla, “Real-Time Obstacle Avoidance Using Harmonic Potential Functions,” 1992. doi: 10.1109/70.143352.

@@

%\bibitem{c46} A. H. Qureshi et al., “Adaptive Potential guided directional-RRT*,” in Proc. 2013 IEEE International Conference on Robotics and Biomimetics (ROBIO), Shenzhen, China, Dec. 2013, pp. 1887–1892. doi: 10.1109/ROBIO.2013.6739744.

@@

%\bibitem{gammell2014informed} J. D. Gammell, S. S. Srinivasa, and T. D. Barfoot, “Informed RRT*: Optimal sampling-based path planning focused via direct sampling of an admissible ellipsoidal heuristic,” in Proc. of the 2014 IEEE/RSJ International Conference on Intelligent Robots and Systems, Chicago, IL, USA, Sep. 2014, pp. 2997–3004. doi: 10.1109/IROS.2014.6942976.
%
%	
%\bibitem{IDEASLab2023}
%IDEAS Lab, "Motion and Path Planning," presented at Purdue University, 2023. [Online]. Available: \url{https://ideas.cs.purdue.edu/research/robotics/planning/}. Accessed on: Jan. 9, 2024.
%

\bibitem{c24} J. Nakanishi, R. Cory, M. Mistry, J. Peters, and S. Schaal, “Comparative experiments on task space control with redundancy resolution,” in Proc. 2005 IEEE/RSJ Int. Conf. on Intelligent Robots and Systems, Edmonton, Alta., Canada, 2005, pp. 3901–3908. doi: 10.1109/IROS.2005.1545203.

\bibitem{c25} M. H. Raibert and J. J. Craig, “Hybrid Position/Force Control of Manipulators,” Journal of Dynamic Systems, Measurement, and Control, vol. 103, no. 2, pp. 126–133, Jun. 1981. doi: 10.1115/1.3139652.

\bibitem{c26} T. Yoshikawa, “Dynamic hybrid position/force control of robot manipulators--Description of hand constraints and calculation of joint driving force,” IEEE J. Robot. Automat., vol. 3, no. 5, pp. 386–392, Oct. 1987. doi: 10.1109/JRA.1987.1087120.

\bibitem{c27} O. Khatib, “A unified approach for motion and force control of robot manipulators: The operational space formulation,” IEEE J. Robot. Automat., vol. 3, no. 1, pp. 43–53, Feb. 1987. doi: 10.1109/JRA.1987.1087068.

\bibitem{c28} N. Hogan, “Impedance Control: An Approach to Manipulation,” in Proc. 1984 American Control Conf., San Diego, CA, USA, Jul. 1984, pp. 304–313. doi: 10.23919/ACC.1984.4788393.

\bibitem{c30} L. Lajpah and T. Petri, “Obstacle Avoidance for Redundant Manipulators as Control Problem,” in Serial and Parallel Robot Manipulators - Kinematics, Dynamics, Control and Optimization, S. Kucuk, Ed. InTech, 2012. doi: 10.5772/32651.

\bibitem{c31} R. Colbaugh and K. Glass, “Cartesian control of redundant robots,” J. Robotic Syst., vol. 6, no. 4, pp. 427–459, Aug. 1989. doi: 10.1002/rob.4620060409.

@@

\bibitem{c34} L. Sciavicco and B. Siciliano, “A solution algorithm to the inverse kinematic problem for redundant manipulators,” IEEE J. Robot. Automat., vol. 4, no. 4, pp. 403–410, Aug. 1988. doi: 10.1109/56.804.

\bibitem{c35} L. Sciavicco and B. Siciliano, “Solving the Inverse Kinematic Problem for Robotic Manipulators,” in RoManSy 6, A. Morecki, G. Bianchi, and K. Kedzior, Eds., Boston, MA: Springer US, 1987, pp. 107–114. doi: 10.1007/978-1-4684-6915-8\_9.

\bibitem{c36} O. Egeland, “Task-space tracking with redundant manipulators,” IEEE J. Robot. Automat., vol. 3, no. 5, pp. 471–475, Oct. 1987. doi: 10.1109/JRA.1987.1087118.

\bibitem{c37} H. Seraji, “Configuration control of redundant manipulators: theory and implementation,” IEEE Trans. Robot. Automat., vol. 5, no. 4, pp. 472–490, Aug. 1989. doi: 10.1109/70.88062.

\bibitem{c39} B. Siciliano and O. Khatib, Eds., Springer Handbook of Robotics. in Springer Handbooks. Cham: Springer International Publishing, 2016. doi: 10.1007/978-3-319-32552-1.

\bibitem{c41} L. Zlajpah and B. Nemec, “Kinematic control algorithms for on-line obstacle avoidance for redundant manipulators,” in Proc. IEEE/RSJ International Conference on Intelligent Robots and Systems, Lausanne, Switzerland, 2002, pp. 1898–1903. doi: 10.1109/IRDS.2002.1044033.

\bibitem{c42} T. Petrič and L. Žlajpah, “Smooth continuous transition between tasks on a kinematic control level: Obstacle avoidance as a control problem,” Robotics and Autonomous Systems, vol. 61, no. 9, Art. no. 9, Sep. 2013. doi: 10.1016/j.robot.2013.04.019.

\bibitem{c48} T. Zhu, J. Mao, L. Han, C. Zhang, and J. Yang, “Real-Time Dynamic Obstacle Avoidance for Robot Manipulators Based on Cascaded Nonlinear MPC With Artificial Potential Field,” IEEE Trans. Ind. Electron., pp. 1–11, 2023. doi: 10.1109/TIE.2023.3306405.

\bibitem{c50} Y. Chen, L. Chen, J. Ding, and Y. Liu, “Research on Real-Time Obstacle Avoidance Motion Planning of Industrial Robotic Arm Based on Artificial Potential Field Method in Joint Space,” Applied Sciences, vol. 13, no. 12, p. 6973, Jan. 2023. doi: 10.3390/app13126973.

\bibitem{c51} S. M. LaValle, Planning Algorithms. Cambridge: Cambridge University Press, 2006.

\bibitem{siciliano2016springer} B. Siciliano and O. Khatib, Eds., Springer Handbook of Robotics, in Springer Handbooks. Cham: Springer International Publishing, 2016. doi: 10.1007/978-3-319-32552-1.

\bibitem{dai2022review} Y. Dai, C. Xiang, Y. Zhang, Y. Jiang, W. Qu, and Q. Zhang, “A Review of Spatial Robotic Arm Trajectory Planning,” Aerospace, vol. 9, p. 361, Jul. 2022, doi: 10.3390/aerospace9070361.

\bibitem{gottschalk1996obbtree} S. Gottschalk, M. C. Lin, and D. Manocha, “OBBTree: a hierarchical structure for rapid interference detection,” in Proceedings of the 23rd Annual Conference on Computer Graphics and Interactive Techniques, ACM, Aug. 1996, pp. 171–180. doi: 10.1145/237170.237244.

\bibitem{vandenbergen1997efficient} G. van den Bergen, “Efficient Collision Detection of Complex Deformable Models using AABB Trees,” Journal of Graphics Tools, vol. 2, no. 4, pp. 1–13, 1997. doi: 10.1080/10867651.1997.10487480.

\bibitem{chen2018path} G. Chen, D. Liu, Y. Wang, Q. Jia, and X. Zhang, “Path planning method with obstacle avoidance for manipulators in dynamic environment,” International Journal of Advanced Robotic Systems, vol. 15, no. 6, Art. no. 1729881418820223, Nov. 2018, doi: 10.1177/1729881418820223.

\bibitem{puiu2011realtime} D. Puiu and F. Moldoveanu, “Real-time collision avoidance for redundant manipulators,” in Proc. of the 2011 6th IEEE International Symposium on Applied Computational Intelligence and Informatics (SACI), Timisoara, Romania, 2011, pp. 403–408, doi: 10.1109/SACI.2011.5873037.

\bibitem{wurmOctoMap} K. M. Wurm, A. Hornung, M. Bennewitz, C. Stachniss, and W. Burgard, “OctoMap: A Probabilistic, Flexible, and Compact 3D Map Representation for Robotic Systems,” [Details of publication, e.g., in Proc. of the Conference/Journal Name, Year, pp. Page numbers]. [DOI or URL if available].

\bibitem{gao2019flying} F. Gao, W. Wu, W. Gao, and S. Shen, “Flying on point clouds: Online trajectory generation and autonomous navigation for quadrotors in cluttered environments,” Journal of Field Robotics, vol. 36, no. 4, pp. 710–733, 2019, doi: 10.1002/rob.21842.

\bibitem{elfes1989using} A. Elfes, “Using occupancy grids for mobile robot perception and navigation,” Computer, vol. 22, no. 6, pp. 46–57, Jun. 1989, doi: 10.1109/2.30720.

\bibitem{xu2021voxel} Y. Xu, X. Tong, and U. Stilla, “Voxel-based representation of 3D point clouds: Methods, applications, and its potential use in the construction industry,” Automation in Construction, vol. 126, p. 103675, Jun. 2021, doi: 10.1016/j.autcon.2021.103675.

\bibitem{niessner2013realtime} M. Nießner, M. Zollhöfer, S. Izadi, and M. Stamminger, “Real-time 3D reconstruction at scale using voxel hashing,” ACM Trans. Graph., vol. 32, no. 6, pp. 1–11, Nov. 2013, doi: 10.1145/2508363.2508374.

\bibitem{dryanovski2010multivolume} I. Dryanovski, W. Morris, and J. Xiao, “Multi-volume occupancy grids: An efficient probabilistic 3D mapping model for micro aerial vehicles,” in Proc. of the 2010 IEEE/RSJ International Conference on Intelligent Robots and Systems, Taipei, Oct. 2010, pp. 1553–1559. doi: 10.1109/IROS.2010.5652494.

\bibitem{thrun2002probabilistic} S. Thrun, Probabilistic robotics, vol. 45, 2002. Accessed: Jun. 14, 2023. [Online]. Available: https://dl.acm.org/doi/10.1145/504729.504754

\bibitem{luo2018collisionfree} L. Luo et al., “Collision-Free Path-Planning for Six-DOF Serial Harvesting Robot Based on Energy Optimal and Artificial Potential Field,” Complexity, vol. 2018, pp. 1–12, Nov. 2018, doi: 10.1155/2018/3563846.

\bibitem{zhang2021obstacle} W. Zhang, H. Cheng, L. Hao, X. Li, M. Liu, and X. Gao, “An obstacle avoidance algorithm for robot manipulators based on decision-making force,” Robotics and Computer-Integrated Manufacturing, vol. 71, p. 102114, Oct. 2021, doi: 10.1016/j.rcim.2020.102114.

\bibitem{szeliski2021computer} R. Szeliski, “Computer Vision: Algorithms and Applications, 2nd Edition,” Springer, 2021.

\bibitem{rosenfeld1968distance} A. Rosenfeld and J. L. Pfaltz, “Distance functions on digital pictures,” Pattern Recognition, vol. 1, no. 1, pp. 33–61, Jul. 1968, doi: 10.1016/0031-3203(68)90013-7.

\bibitem{felzenszwalb2012distance} P. F. Felzenszwalb and D. P. Huttenlocher, “Distance Transforms of Sampled Functions,” Theory of Comput., vol. 8, no. 1, pp. 415–428, 2012, doi: 10.4086/toc.2012.v008a019.

\bibitem{dryanovski2010multivolume} I. Dryanovski, W. Morris, and J. Xiao, “Multi-volume occupancy grids: An efficient probabilistic 3D mapping model for micro aerial vehicles,” in 2010 IEEE/RSJ International Conference on Intelligent Robots and Systems, Taipei: IEEE, Oct. 2010, pp. 1553–1559, doi: 10.1109/IROS.2010.5652494.

>>>>

Motion planning~\cite{c52} is a technique in robotics, that is used to calculate joint changes leading manipulators from initial to a target configuration, while addressing constraints and optimization criteria. This task is facilitated by the manipulators' redundant degrees of freedom (DOF), enabling it to undertake various configurations to not only reach their End Effector (EE) target but also optimize for secondary objectives such as obstacle avoidance and minimizing joint torques~\cite{siciliano1990kinematic}.

While global motion planning techniques provide comprehensive solutions by examining the entire configuration space, they fall short in terms of smoothness and real-time application, making them less ideal for dynamic settings~\cite{lavalle1998rapidly, gammell2015batch, karaman2010incremental,kuffner2000rrt}. Conversely, local planning methods, particularly inverse kinematics~\cite{c29,c38} and quadratic programming~\cite{c21,c23, haviland2021neo}, offer prompt, smooth trajectories suitable for real-time operations. However, these methods are prone to fall into local minima due to their incremental planning approach.

@@

Our approach utilizes occupancy voxel grids~\cite{han2018dynamic} to enable safe and dynamic navigation for robot manipulators in changing environments. By representing the workspace with voxels and calculating repulsive velocities based on proximity to obstacles, our method allows the robot to determine safe movement directions and velocities in real-time. Repulsive velocities gain strength as the robot approaches an obstacle, guiding it to move away from potential collisions, and weaken when the robot is at a safe distance, maintaining an optimal distance from hazards. This locally-calculated repulsive field ensures the robot moves safely and efficiently in dynamic environments.

@@

%\bibitem{siciliano2010robot} B. Siciliano, L. Sciavicco, L. Villani, and G. Oriolo, Robot. Model. Plan. Control, 2010, pp. 161–189. [Online]. Available: http://link.springer.com/10.1007/978-1-84628-642-1\_4

@@

@@

@@

@@

\bibitem{c30} L. Žlajpah and T. Petrič, “Obstacle Avoidance for Redundant Manipulators as Control Problem,” in Serial and Parallel Robot Manipulators - Kinematics, Dynamics, Control and Optimization, S. Kucuk, Ed. InTech, 2012. doi: 10.5772/32651.

@@

\bibitem{c41} L. Žlajpah and B. Nemec, “Kinematic control algorithms for on-line obstacle avoidance for redundant manipulators,” in Proc. IEEE/RSJ International Conference on Intelligent Robots and Systems, Lausanne, Switzerland, 2002, pp. 1898–1903. doi: 10.1109/IRDS.2002.1044033.
